Phase paper outline

### 2014-05-21 Manuscript/Phase_detectors_outline.tex
added to intro

>>>>

Homeostasis is maintained by numerous interacting physiological control systems. Physiological systems are responsible for controlling a given output variable in response to one or more input variables. For example Heart rate is controlled by the autonomic nervous system to maintain blood pressure. Nonlinear responses between input and output in physiological systems are ubiquitous. Furthermore there are inherent delays in the response of each system because of inter and intra cellular signalling events. These nonlinearities
